Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-08 tese2/architecture.tex
[RFT] improving architecture

@@

The requirements for our web application are:

\begin{itemize}
 \item Text, Audio and Video communication using \ac{WebRTC}.
 \item Ability to record and playback interactive multimedia.
 \item Create annotations over video and voice content.
 \item Enrich communications by overlaying multiple media types.
 \item Search and navigate through annotations and contents.
 \item Ability to create and share time links among users.
 \item Mix multiple user streams into a single stream.
 \item Sound detection for showing the current speaker.
 \item Structure presentation of the content.
 \item Collaborative text edition.
 \item Easy interface for content creation and synchronization. 
\end{itemize}

@@

	Moreover we allow clients to discover chat rooms and other clients by navigating on the web pages provided by our web server. In addition users can create rooms for multi-party audio and video communication communication which is achieved by using \ac{WebRTC}'s \emph{MediaStream} and \emph{PeerConnection}.
        %RP falas em peerconnection, mas na figura 3.1 apenas há um cliente, o que obviamente impede mostrar a comunicação entre peers.
        %RP acho que podes fazer outro diagrama com a comunicação entre os vários componentes, onde apareceriam vários clientes. A aí indicas o tipo de ligação entre cada par de componentes (HTTP, PeerConnectino, websocket, MediaStream ...)

	Furthermore, chat rooms can be public or private. Public chat rooms are moderated by a group of clients which initially consistes only of the room creator. This type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will only be visible to a defined list of clients or can be accessed by clients that have a link for that conference room.

@@

\item \underline{Application module} - responsible for providing information about the relevant modules (\emph{NAT Traversal} and \emph{Signaling}) and user interface to the \emph{Client}.

\item \underline{Signaling module} - responsible for \emph{Client} and \emph{Stream} coordination.

 \item \underline{NAT Traversal module} - used by \emph{Client} and \emph{Stream} modules during the \emph{Signaling} phase which ends by establishing the connection between them.

 \item \underline{Stream module} - responsible to deliver and receive multimedia content from the \emph{Client}.

 \item \underline{Storage module} - provides two main functionalities: store the model information and media recorded. This is the single module responsible for persistent storage. It stores user and communication data as well as all the data required among user sessions. It is also use to store all the communication streams, so that they can be viewed later.

 \item \underline{Client module} - responsible for the interaction with the user.

@@

% Each room will be associated to multiple Media-Types, interactive and non-interactive, discrete and continuous. This media types can be structured with chains of events. Some components of the user interface may not be synchronized to all participants, for example an help or suggestion window.

@@

@@

@@

Due to the fact we are going to use \ac{KMS} as streaming server solution, we could choose \emph{NodeJS} or any \emph{Java} based web framework for implementing our web application server. One of our criteria for choosing the web framework is the ability to follow the \ac{MVC} paradigm which can help us to organize our code. Without any strong reason we have decided to implement our web server with the \emph{PlayFramework}\footnote{\url{https://www.playframework.com/}(acessed March 25, 2016)} using \emph{Java}.
%RP nem sequer por estares mais familiarizado com java ou a playframework? Ou porque querias aprender? Alguma razão há-de ter havido

@@

\begin{table}[H]
\centering
	\caption{Application Architecture}
	\label{table:apparch}
    \begin{tabular}{cccccccc@{}m{0pt}@{}}
	\hline 
\multicolumn{8}{|c|}{\cellcolor{Gray}Application}  &\\[12pt]\cline{1-5}\cline{7-7}
\multicolumn{1}{|c|}{jQuery} & \multicolumn{1}{c|}{HTML5} & \multicolumn{1}{c|}{CSS3} & \multicolumn{1}{c|}{Signaling} & \multicolumn{1}{c|}{~~~~~ot.js~~~~~} & \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} & \multicolumn{1}{c|}{adapter.js} &   \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} &\\[12pt]\hline
\multicolumn{1}{|c|}{HTTP} & \multicolumn{2}{c|}{User Interface}  & \multicolumn{3}{c|}{WebSocket}    & \multicolumn{2}{c|}{WebRTC}      &\\[12pt]\hline
\end{tabular}
\end{table}

@@

The synchronization between multimedia elements will be performed through chains of \emph{JavasSript} events or by specifying the interval of time which time content must be visible. Other animations can be implemented with \ac{SVG} embedded on \ac{HTML}.
%RP Caiu do céu! Tens de explicar e ligar melhor a sequencia de texto

>>>>

\section{Requirements}
In a general way our system's goal is to provide a multi-party video and audio conference environment that supports chat, time manipulation, collaborative text edition and hyper-content creation.

@@

For our system, the goals include:

\begin{itemize}
 \item \textbf{Instant Messaging} - Our application must provide a simple way to send instant text messages to the conference participants.
 \item \textbf{Room management} - Conference rooms can be public or private. Public chat rooms are moderated by a group of clients which initially consists only of the room creator. This type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will only be visible to a defined list of clients or can be accessed by clients that have a link for that conference room.
 \item \textbf{Stream Recording} - Ability to recording and playback recorded video including all the hyper-content displayed at that time.
 \item \textbf{Stream Composition} - Our streaming server must support mixing multiple user streams into a single stream. The sound played on clients must be the composed sound of all participants but the video played can be switched to the individual or group view.
 \item \textbf{Time annotations} - Our application must give the possibility to create annotations associated to a specified time and support viewing them on a time-line. 
 \item \textbf{Content Overlay} - Our system must allow users to superimpose hyper-content to video given a range of time. This content can be continuous or discrete and interactive or non interactive.
 \item \textbf{Search} - Unified search every objects related to a conference room such as hyper-content, time annotations and users.
 \item \textbf{Content Sharing} - Our application must have the ability to share files and time links among users.
 \item \textbf{Active talker detection} - The system must enable sound detection for showing the current speaker.
 \item \textbf{Collaboration} - The web application must provide a collaborative text edition tool.
 \item \textbf{QR Code detection} - The system must interpret \emph{QR codes} in order to ease content creation.
 \item \textbf{NAT Traversal} - The system's services must be available to users that are inside a private network.
 \item \textbf{Fault tolerance} - Our system's must use a database that supports data replication.
 \item \textbf{Scalability} - Our system must be horizontally scalable, which means that load must be distributed across web, streaming and database servers.
\end{itemize}

@@

	Moreover we allow clients to discover chat rooms and other clients by navigating on the web pages provided by our web server. In addition users can create rooms for multi-party audio and video communication communication which is achieved by using \ac{WebRTC}'s \emph{PeerConnection}.
        %RP falas em peerconnection, mas na figura 3.1 apenas há um cliente, o que obviamente impede mostrar a comunicação entre peers.
        %RP acho que podes fazer outro diagrama com a comunicação entre os vários componentes, onde apareceriam vários clientes. A aí indicas o tipo de ligação entre cada par de componentes (HTTP, PeerConnectino, websocket, MediaStream ...)

@@

\item \textbf{Application module} - responsible for providing information about the relevant modules (\emph{NAT Traversal} and \emph{Signaling}) and user interface to the \emph{Client} in the form of web pages in \ac{HTML} and \emph{JavaScript} libraries through \ac{HTTP}.

\item \textbf{Signaling module} - responsible for \emph{Client} and \emph{Stream} coordination which will be performed using \emph{WebSockets}.

 \item \textbf{NAT Traversal module} - \ac{STUN} and \ac{TURN} techniques used by \emph{Client} and \emph{Stream} modules during the \emph{Signaling} phase which ends by establishing the connection between them.

 \item \textbf{Stream module} - responsible to deliver and receive multimedia content from the \emph{Client} using \ac{WebRTC}.

 \item \textbf{Storage module} - provides two main functionalities: store the model information and media recorded. This is the single module responsible for persistent storage. It stores user and communication data as well as all the data required among user sessions. It is also use to store all the communication streams, so that they can be viewed later.

 \item \textbf{Client module} - responsible for the interaction with the user.

@@

@@

	\subsection{Security and authorization}

@@

\subsection{Client connections}
	Although the delegation of processing work to clients can improve our system's scalability, we are concerned about using the least resources possible on the client side, as huge resource consumption may drain battery very fast or may even be impossible to run on mobile devices. We are aware that streaming video from clients is already a very intensive task which we cannot avoid but can improve by delegating the most intensive tasks to our servers.

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.4\textwidth]{figures/central.pdf}
	\caption{Centralized Connections}
	\label{fig:central}
	\end{figure}

	In this context, each client must only have one \emph{PeerConnection} to our streaming server and content shown to them is changed on demand either being it an individual or a composite view. This approach is centralized, as seen on figure \ref{fig:central}.

	The same can be applied to instant message delivery, each client must have only one \emph{WebSocket} connection to the application server which consequently relays the messages to other users.

	Relaying instant messages from clients through the our web servers is easier if all clients are connected to the same server because all messages can be directly delivered without sending messages across multiple web servers.

	In the context of this thesis, we will not implement sending messages across web servers but, in order to allow our system to scale, we will consider that all conference participants are connected to the same server and our system is scaled by having conference rooms distributed across different servers.

\subsection{Software choices}

@@

Due to the fact we are going to use \ac{KMS} as streaming server solution, we could choose \emph{NodeJS} or any \emph{Java} based web framework for implementing our web application server. One of our criteria for choosing the web framework is the ability to follow the \ac{MVC} paradigm which can help us to organize our code. We have decided to implement our web server with the \emph{PlayFramework}\footnote{\url{https://www.playframework.com/}(acessed March 25, 2016)} using \emph{Java} because of our previous experience with it.

@@

\begin{table}[H]
\centering
	\caption{Application Architecture}
	\label{table:apparch}
    \begin{tabular}{cccccccc@{}m{0pt}@{}}
	\hline 
\multicolumn{8}{|c|}{\cellcolor{Gray}Application}  &\\[12pt]\cline{1-5}\cline{7-7}
\multicolumn{1}{|c|}{jQuery} & \multicolumn{1}{c|}{HTML5} & \multicolumn{1}{c|}{CSS3 (Bootstrap)} & \multicolumn{1}{c|}{Signaling} & \multicolumn{1}{c|}{~~~~~ot.js~~~~~} & \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} & \multicolumn{1}{c|}{adapter.js} &   \multicolumn{1}{c|}{\cellcolor{Gray}~~~~~~~~~~~~~~~} &\\[12pt]\hline
\multicolumn{1}{|c|}{HTTP} & \multicolumn{2}{c|}{User Interface}  & \multicolumn{3}{c|}{WebSocket}    & \multicolumn{2}{c|}{WebRTC}      &\\[12pt]\hline
\end{tabular}
\end{table}

@@

With respect to displaying content, the synchronization between multimedia elements will be performed through chains of \emph{JavasSript} events or by specifying the interval of time which time content must be visible. Other animations can be implemented with \ac{SVG} embedded on \ac{HTML}.
%RP Caiu do céu! Tens de explicar e ligar melhor a sequencia de texto
